Enhanced proximity effect in zigzag-shaped Majorana Josephson junctions.

### 2019-03-11 paper/snakemajoranas.tex
start slight rewrite of intro

%%██████████████████████████████████████████████████████████████████████████
%%██ Introduction
%%██████████████████████████████████████████████████████████████████████████
\section{Introduction}
\comment{Hybrid NS structures become topological and are useful for TQC.}
A hybrid structure containing a semiconductor with strong spin-orbit coupling coupled to a superconductor, inside a magnetic field becomes topological within the right parameter regime ($E_\text{Z}^2>\mu^2+\Delta^2$ for a simple nanowire), and Majorana bound states appear on its edges~\cite{Lutchyn2010,Oreg2010}.
Majorana bound states are a promising candidate to form the basis of a stable platform for topological quantum computing. ~\cite{Alicea2012,Beenakker2013,Beenakker2016,Leijnse2012}
The current experimental effort ~\cite{Mourik2012,Das2012,Deng2012,Churchill2013,Zhang2018} focuses on creating pairs of Majorana bound states in hybrid normal-superconductor (NS) nanowire structures.

\comment{SNS junctions also work and require smaller field.}
Recently, a modified setup has been proposed\cite{Pientka2017,Hell2017} relying on a superconductor-normal-superconductor (SNS) junction to lower the critical magnetic field $B_\textrm{c}$ by introducing a superconducting phase difference $\phi$.
When both NS interfaces are transparent the SNS junction enters the topological phase at $\phi=\pi$ at any finite $B$ field.
Two groups~\cite{Fornieri2018,Ren2018} have realized this system experimentally but did not yet observe a hard induced gap.

>>>>

%%██████████████████████████████████████████████████████████████████████████
%%██ Introduction
%%██████████████████████████████████████████████████████████████████████████
\section{Introduction}
\comment{Hybrid NS structures become topological and are useful for TQC.}
A hybrid structure containing a semiconductor with strong spin-orbit coupling coupled to a superconductor can become topological upon application of a magnetic field stronger than a critical field $B_\textrm{crit}$, with Majorana bound states appearing on its edges~\cite{Lutchyn2010,Oreg2010}.
Majorana bound states are a promising candidate to form the basis of a stable platform for topological quantum computing. ~\cite{Alicea2012,Beenakker2013,Beenakker2016,Leijnse2012}
Much of the experimental effort ~\cite{Mourik2012,Das2012,Deng2012,Churchill2013,Zhang2018} currently focus on creating pairs of Majorana bound states in hybrid normal-superconductor (NS) nanowire structures.

\comment{SNS junctions also work and require smaller field.}
Recently, a modified setup has been proposed\cite{Pientka2017,Hell2017} relying on a superconductor-normal-superconductor (SNS) junction to lower the critical magnetic field $B_\textrm{c}$ by introducing a superconducting phase difference $\phi$.
When both NS interfaces are transparent the SNS junction enters the topological phase at $\phi=\pi$ at any finite $B$ field.
Two groups~\cite{Fornieri2018,Ren2018} have realized this system experimentally, but did not yet observe a hard induced superconducting gap.
